Double White Dwarf Mergers with CASTRO\\ I. Methodology and Code Verification

### 2013-08-02 paper.tex
more methods

\subsection{Initial Models and Microphysics}

@@

>>>>

\subsection{Microphysics}

\subsection{Initial Models}

@@

We map the 1-d model onto the 3-d Cartesian grid by taking density,
temperature, and composition as the independent variables,
interpolating these to the cell-centers, and then calling the equation
of state to initialize the remaining terms.  The velocity is taken to
be zero in the rotating frame initially.
